% !TeX spellcheck = en_US
% Preamble
% ---
\documentclass{article}

% Packages
% ---
\usepackage{amsmath} % Advanced math typesetting
\usepackage[utf8]{inputenc} % Unicode support (Umlauts etc.)
\usepackage[USenglish]{babel}
\usepackage{listings} % Source code formatting and highlighting
\usepackage{amssymb} % Math symbols
\usepackage{enumitem} % Numbering items
\usepackage[margin=0.75in]{geometry} % Change margins
\usepackage{parskip}
\usepackage{indentfirst}
\usepackage{enumitem}

% Change hyperlink style
\usepackage[
	colorlinks = true,
	linkcolor = blue,
	urlcolor  = blue,
	citecolor = blue,
	anchorcolor = blue,
]{hyperref}

% Section heading
\newenvironment{sectionHeading}{
	\hrule height 1.5pt
	\vspace{0.75em}
}

% Heading for organization; role; events
\newenvironment{itemHeading}{
	\setlength{\parindent}{2em}
}

\setlength{\parindent}{2em}
\setlength{\parskip}{0em}
\setlength{\baselineskip}{0em}
\setlist{
	leftmargin=4.5em,
	topsep=0em
}

\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\sfdefault}{ppl} % Palantino is the default serif font

\newenvironment{sans}{\fontfamily{phv}\selectfont}{\par}	% Sans serif: Helvetica
\newenvironment{serif}{\fontfamily{ppl}\selectfont}{\par}	% Serif: Palatino

\pagenumbering{gobble}	% Turn off page numbering

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}
	\begin{center}
		{\begin{sans}
				\huge \textbf{Samantha Yu}\\
		\end{sans}}
		{\small
			Website: {\color{blue}\href{http://samanthayu.github.io/}{samanthayu.github.io}}\ \ \textbullet
			\ \ Email: samanthayu36@gmail.com
		}
	\end{center}
	
	\subsection*{\begin{sans}Education\end{sans}} % * Removes the section numbers
	\begin{sectionHeading}\end{sectionHeading}
	\begin{serif}
		\textbf{Simon Fraser University} \textit{(Sept. 2015 - April 2019)}
		\begin{itemize}
			\item Bachelor of Science: Computing Science Major
			\item \textbf{Relevant Courses:} CMPT 225 - Data Structures; CMPT 295 - Introduction to Computer Systems
		\end{itemize}
	\bigskip
	
	\textbf{Technical Skills:} Java, C, C++, x86-64 Assembly, Python, MATLAB, \LaTeX, Apache, JavaScript, HTML/CSS
	\end{serif}
	
	\subsection*{\begin{sans}Projects\end{sans}} % * Removes the section numbers
	\begin{sectionHeading}\end{sectionHeading}
	Automated Window Cleaner: \textbf{Java} \textit{(Sept. 2015 - Dec. 2015)}
	\begin{itemize}
		\item Simulated a window cleaner and its suction cups moving on a skyscraper
	\end{itemize}
	\bigskip

	Universal Motor for Vacuum Cleaner \textit{(May 2015 - June 2015)}
	\begin{itemize}
		\item Built an universal motor to study electromagnetism and back-EMF
	\end{itemize}
	\bigskip
	
	Paint Program: \textbf{Java} \textit{(Aug. 2014 - Jan. 2015)}
	\begin{itemize}
		\item Incorporated the concept of double buffering
		\item Implemented the capability to add, delete, and modify layers
	\end{itemize}
	\bigskip
	
	BC Senior Girls Volleyball Provincials Website: \textbf{HTML/CSS} \textit{(Oct. - Nov. 2013)}
	\begin{itemize}
		\item Served sixteen teams and their supporters from all over British Columbia
		\item Designed overall layout including templates, drop-down menu and footer menu
	\end{itemize}
	
	\subsection*{\begin{sans}Extracurricular Activities\end{sans}}
	\begin{sectionHeading}\end{sectionHeading}
	SFU Satellite Design Club \textit{(Feb. 2016 - Present)}
	\begin{itemize}
		\item Programming onboard computer for a weather balloon and a satellite
		\item Building a mobile app to display telemetry and control the camera on the weather balloon
	\end{itemize}
	\bigskip
	
	Women in Computing Science: Website Manager \textit{(Sept. 2015 - Present)}
	\begin{itemize}
		\item Organized the Try/CATCH 2016 conference to introduce 47 high school girls to computing science
		\item Transferring content from old website to updated website
	\end{itemize}
	\bigskip

	IEEE Game Development Club \textit{(Sept. 2015 - Dec. 2015)}
	\begin{itemize}
		\item Learned to program video games with Irrlicht, open source game engine in C++
	\end{itemize}

	\subsection*{\begin{sans}Achievements\end{sans}}
	\begin{sectionHeading}\end{sectionHeading}
	Simon Fraser University
	\begin{itemize}
		\item Simon Fraser University Open Scholarship \textit{(May 2016)}
	\end{itemize}
	\bigskip
	
	Micosoft
	\begin{itemize}
		\item \#DevMov Competition Top Prize: Surface Pro 4 \textit{(June 2016)}
	\end{itemize}
	\bigskip
	
	BC Ministry of Education
	\begin{itemize}
		\item Dogwood District/Authority Award for Computer Programming \textit{(April 2015)}
	\end{itemize}
	\bigskip
	
	\subsection*{\begin{sans}Work Experience\end{sans}}
	\begin{sectionHeading}\end{sectionHeading}
	Kumon Assistant \textit{(Sept. 2014 - Aug. 2015)}
	\begin{itemize}
		\item Tutored children of various levels in math and English
	\end{itemize}
	\bigskip
\end{document}